\sysfull

### 2018-08-05 paper/asplos19/background.tex
section 2

\textbf{What Hardware does \sys Target.} \sys is designed for the demands of existing and future \emph{tiny embedded energy-harvesting platforms} based around general purpose, commodity computing components~\cite{wisp,msp430datasheet}. \sys targets a device with a memory system that has fast, byte-addressable volatile and non-volatile memory; in particular, our target platform, WISP~\cite{wisp}, is equipped with a mixture of SRAM and FRAM. \sys leverages hardware support for fast, bulk-copying between memories via DMA~\cite{msp430datasheet}. \sys does not require architectural additions to commodity processors as in~\cite{su_date_2017,hicks_isca_2017,quickrecall,nvp}.

@@

\textbf{Frequent Non-volatile Memory Access.}  \note{I want to emphasize again that we do not evaluate NV memory accesses} Previous systems frequently access the non-volatile memory directly, which is a potential source of inefficiency. Checkpointing systems copy all volatile state~\cite{dino, mementos, ratchet, hicks_isca_2017} to non-volatile memory at every checkpoint.  Task-based models, which do not take checkpoints, back up a subset of non-volatile data to maintain memory consistency using, e.g., redo-logging.  Table~\ref{table:chechpoint_comparison} summarizes the data that gets copied to and from the non-volatile memory in service of memory consistency and progress preservation.  Ratchet~\cite{ratchet} and Clank~\cite{hicks_isca_2017}, which require all memory to be non-volatile, perform high-frequency non-volatile memory accesses, checkpointing frequently.

>>>>

\textbf{Target Hardware of \sys.} \sys is designed for the demands of existing and future \emph{tiny embedded energy-harvesting platforms} based around general purpose, commodity computing components~\cite{wisp,msp430datasheet}. \sys targets a device with a memory system that has fast, byte-addressable volatile and non-volatile memory; in particular, our target platform, WISP~\cite{wisp}, is equipped with a mixture of SRAM and FRAM. \sys leverages hardware support for fast, bulk-copying between memories via DMA~\cite{msp430datasheet}. \sys does not require architectural additions to commodity processors as in~\cite{su_date_2017,hicks_isca_2017,quickrecall,nvp}.

@@

\textbf{Direct Non-volatile Memory Access.}  \note{I want to emphasize again that we do not evaluate NV memory accesses} Previous systems frequently access the non-volatile memory directly, which is a potential source of inefficiency. Checkpointing systems copy all volatile state~\cite{dino, mementos, ratchet, hicks_isca_2017} to non-volatile memory at every checkpoint.  Task-based models, which do not take checkpoints, back up a subset of non-volatile data to maintain memory consistency using, e.g., redo-logging.  Table~\ref{table:chechpoint_comparison} summarizes the data that gets copied to and from the non-volatile memory in service of memory consistency and progress preservation.  Ratchet~\cite{ratchet} and Clank~\cite{hicks_isca_2017}, which require all memory to be non-volatile, perform high-frequency non-volatile memory accesses, checkpointing frequently. On the other hand, \sys accesses non-volatile memory by using only DMA and without CPU intervention: \sys moves a batch of variables from non-volatile memory into volatile memory and programs are only allowed to access individual variables in volatile memory directly.
